---
title: "20220825_workflow_KUmobning"
output: html_document
date: "2022-08-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [0.0.] Load necessary packages
```{r message=FALSE}
base::library(tidyverse)
base::library(here)
```

## [1.0.] Read data
```{r}
fs <- base::list.files(
      path = here::here("data"),
      full.names = TRUE
    ) %>%
  stringr::str_subset("csv")

tab <- readr::read_delim(
    file = fs,
    delim = ";",
    skip = 0,
    col_names = TRUE,
    col_types = readr::cols(
      .default = readr::col_double(),
      institute = readr::col_character(),
      id = readr::col_character(),
      source_slide = readr::col_skip(),
      source = readr::col_skip()
    ),
    locale = locale(decimal_mark = ",")
  )
```

## [1.1.] Evaluate
```{r}
tab %>%
  tidyr::drop_na() %>%
  dplyr::group_by(institute,year,id) %>%
  dplyr::summarise(count = dplyr::n()) %>%
  dplyr::filter(count > 1L)
```

## [2.0.] Calculate relative cases
```{r}
ys <- base::c("2016","2019","2022")
tab_wide_ <- tab %>%
  dplyr::select(-cases_relative) %>%
  tidyr::pivot_wider(
      names_from = "id",
      values_from = "cases_absolute"
    ) %>%
  dplyr::mutate(
      all_cases_rel = 100*all_cases/all_answers,
      year = base::factor(
        x = year,
        levels = ys,
        ordered = TRUE
      )
    )
```

## [2.1.] Set object levels
```{r}
levs <- tab_wide_ %>%
  dplyr::filter(
      year == "2022" &
      institute != "KU"
    ) %>%
  dplyr::arrange(
      dplyr::desc(all_cases_rel)
    ) %>%
  dplyr::pull(institute)

tab_wide <- tab_wide_ %>%
  dplyr::mutate(
    institute = base::factor(
      x = institute,
      levels = base::c("KU",levs),
      ordered = TRUE
    )
  )

std <- tab_wide_ %>%
  dplyr::filter(
      year == "2022" &
      institute == "KU"
    ) %>%
  dplyr::pull(all_cases_rel)
```

## [2.2.] Plot instances
```{r}
ggplot2::ggplot(
      data = tab_wide,
      mapping = aes(
        y = year,
        x = all_cases_rel,
        fill = year
      )
    ) +
  geom_bar(
      stat = "identity",
      colour = "black"
    ) +
  geom_text(
      mapping = aes(
          label = all_cases
        ),
      hjust = -0.25,
      size = 3
    ) +
  geom_vline(
      xintercept = std,
      linetype = "dashed"
    ) +
  scale_y_discrete(
      position = "right"
    ) +
  scale_x_continuous(
      limits = base::c(0,16)
    ) +
  scale_fill_manual(
      limits = ys,
      breaks = ys,
      values = base::c("white","grey50","black")
    ) +
  facet_wrap(
      facets = . ~ institute,
      ncol = 1,
      strip.position = "left"
    ) +
  theme_bw() +
  theme(
      panel.spacing = grid::unit(0.1,"lines"),
      aspect.ratio = 1/3,
      axis.title = element_blank(),
      legend.position = "none"
    )
```

## [2.3.] Print plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_allInstancesRatio",
          ".", ext
        ),
      plot = ggplot2::last_plot(),
      device = ext,
      dpi = 300,
      width = 3,
      height = 6
    )
  }
```

## [3.0.] Evaluate
#### Reproduce the original 'victim_acted' 
#### evaluate with tp = "cases_relative"
```{r}
tab_all <- tab %>%
  tidyr::pivot_longer(
      cols = tidyselect::contains("_"),
      names_to = "cases_type",
      values_to = "value"
    ) %>%
  dplyr::mutate(
      new_id = purrr::pmap_chr(
        .l = base::list(id,cases_type),
        .f = function(id,tp){
          suf = stringr::str_replace(tp,".*_(.{3}).*","\\1")
          return(
            base::paste(id,suf,sep = "_")
          )
        }
      )
    ) %>%
  dplyr::select(-id,-cases_type) %>%
  tidyr::pivot_wider(
      names_from = "new_id",
      values_from = "value"
    ) %>%
  dplyr::filter(year == 2022)

tab_all %>%
  dplyr::mutate(
    victim_disengaged = (
      all_cases_abs*(
          A_unsure_rel + A_fear_colleagues_rel + A_fear_leadership_rel +
          A_fear_job_rel + A_no_difference_rel
        )/100
      ),
    victim_acted_all = (
      all_cases_abs*(
          B_discuss_HR_rel + B_discuss_AmrTr_rel + B_discuss_leadership_rel +
          B_discuss_colleagues_rel + B_stop_rel
        )/100
      ),
    other = (
      all_cases_abs*(
          C_other_rel + C_no_answer_rel + unserious_rel
      )/100
    ),
    victim_acted_new = victim_acted_all*(all_cases_abs/(victim_disengaged + victim_acted_all)) - other
  ) %>%
  dplyr::select(victim_acted_abs,victim_acted_new)
```

## [3.1.] Calculate normalized 'victim_acted' parameter
```{r}
tab_norm <- tab_all %>%
  dplyr::mutate(
      all_cases_norm = all_cases_abs - ((unserious_rel/100)*all_cases_abs),
      victim_disengaged = (
        all_cases_norm*(
            A_unsure_rel + A_fear_colleagues_rel + A_fear_leadership_rel +
            A_fear_job_rel + A_no_difference_rel
          )/100
        ),
      victim_acted_all = (
        all_cases_norm*(
            B_discuss_HR_rel + B_discuss_AmrTr_rel + B_discuss_leadership_rel +
            B_discuss_colleagues_rel + B_stop_rel
          )/100
        ),
      other = (
        all_cases_norm*(
            C_other_rel + C_no_answer_rel
        )/100
      ),
      victim_acted_new = victim_acted_all*(
          all_cases_norm/(victim_disengaged + victim_acted_all)
        ) - other
    ) %>%
  dplyr::select(
      institute, year, resolved = resolved_abs,
      all_cases_abs,  all_cases_norm,
      victim_acted = victim_acted_new
    ) %>%
  dplyr::mutate(
      year = base::factor(
          x = year,
          levels = ys,
          ordered = TRUE
        ),
      institute = base::factor(
        x = institute,
        levels = base::c("KU",levs),
        ordered = TRUE
      )
    )
```

## [3.2.] Combine data from all 3 years
```{r}
tab_comb <- tab_wide %>%
  dplyr::filter(
      year != 2022
    ) %>% 
  dplyr::select(
      institute, year, resolved,
      all_cases_abs = all_cases, victim_acted
    ) %>%
  dplyr::mutate(
      all_cases_norm = NA
    ) %>% 
  dplyr::bind_rows(.,tab_norm)
```


## [3.3.] Calculate relative amount of resolved cases
```{r}
tab_resolv <- tab_comb %>%
  dplyr::mutate(
      all_resolved_rel = 100*(resolved/all_cases_abs),
      vic_resolved_rel = 100*(resolved/victim_acted)
    )

std_res <- tab_resolv %>%
  dplyr::filter(
      year == "2022" &
      institute == "KU"
    ) %>%
  dplyr::pull(all_resolved_rel)
```

## [3.4.] Plot 'resolved' instances
```{r}
ggplot2::ggplot(
      data = tab_resolv,
      mapping = aes(
        y = year,
        x = all_resolved_rel,
        fill = year
      )
    ) +
  geom_bar(
      stat = "identity",
      colour = "black"
    ) +
  geom_text(
      mapping = aes(
          label = resolved
        ),
      hjust = -0.25,
      size = 3
    ) +
  geom_vline(
      xintercept = std_res,
      linetype = "dashed"
    ) +
  scale_y_discrete(
      position = "right"
    ) +
  scale_x_continuous(
      limits = base::c(0,60)
    ) +
  scale_fill_manual(
      limits = ys,
      breaks = ys,
      values = base::c("white","grey50","black")
    ) +
  facet_wrap(
      facets = . ~ institute,
      ncol = 1,
      strip.position = "left"
    ) +
  theme_bw() +
  theme(
      panel.spacing = grid::unit(0.1,"lines"),
      aspect.ratio = 1/3,
      axis.title = element_blank(),
      legend.position = "none"
    )
```

## [3.5.] Print plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_resolvedInstancesRatio",
          ".", ext
        ),
      plot = ggplot2::last_plot(),
      device = ext,
      dpi = 300,
      width = 3,
      height = 6
    )
  }
```

## [4.0.] Derive KU-average value for 'vic_resolved_rel' parameter
```{r}
std_res_rel <- tab_resolv %>%
  dplyr::filter(
      year == "2022" &
      institute == "KU"
    ) %>%
  dplyr::pull(vic_resolved_rel)
```

## [4.1.] Calculate relative amount of resolved cases
```{r}
ggplot2::ggplot(
      data = tab_resolv,
      mapping = aes(
        y = year,
        x = vic_resolved_rel,
        fill = year
      )
    ) +
  geom_bar(
      stat = "identity",
      colour = "black"
    ) +
  geom_text(
      mapping = aes(
          label = base::round(victim_acted,digits = 2)
        ),
      hjust = -0.25,
      size = 3
    ) +
  geom_vline(
      xintercept = std_res_rel,
      linetype = "dashed"
    ) +
  scale_y_discrete(
      position = "right"
    ) +
  scale_x_continuous(
      limits = base::c(0,160)
    ) +
  scale_fill_manual(
      limits = ys,
      breaks = ys,
      values = base::c("white","grey50","black")
    ) +
  facet_wrap(
      facets = . ~ institute,
      ncol = 1,
      strip.position = "left"
    ) +
  theme_bw() +
  theme(
      panel.spacing = grid::unit(0.1,"lines"),
      aspect.ratio = 1/3,
      axis.title = element_blank(),
      legend.position = "none"
    )
```

## [4.2.] Print plot
```{r}
for(ext in base::c("pdf", "png")){
    ggplot2::ggsave(
      filename = base::paste0(
          here::here("results/"),
          base::format(base::Sys.time(), "%Y%m%d"),
          "_normResolvedInstancesRatio",
          ".", ext
        ),
      plot = ggplot2::last_plot(),
      device = ext,
      dpi = 300,
      width = 3,
      height = 6
    )
  }
```
